---
title: "pbmc_media_storage"
author: "almutlue"
date: "2019-05-28"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Different media conditions

Pbmc - media storage

**PBMC dataset** from Roche that has been collected to test the influence of media storage on sequencing. It includes 11045 human PBMCs from the same sample, split into 4 batches. All batches have been sequenced together and libraries have been prepared together, but 3 batches have been stored in different media DMSO, CSF and PSC and frozen for 7 days before sequencing. The last batch contains PBMCs from freshly collected blood. Differences between these batches should all derive from media storage, so conditional sources.

```{r libs}
suppressPackageStartupMessages({
  library(dplyr)
  library(CellMixS)
  library(scater)
  library(scran)
  library(variancePartition)
  library(here)
  library(jcolors)
  library(magrittr)
  library(purrr)
  library(diffcyt)
  library(tidyr)
})
```


```{r data}
# data 
data_path <- here::here("data")
out_path <- here::here("output")

# raw data 
#For preprocessing and quality control please check: /code/pbmc_media.rmd
sce <- readRDS(paste0(data_path, "/pbmc_media.rds"))

cols <-c(c(jcolors('pal6'),jcolors('pal8'))[c(1,8,14,5,2:4,6,7,9:13,15:20)],jcolors('pal4'))
names(cols) <- c()

```

# Visualize batch effect
```{r vis batch}
feature_list <- c("sample_type", "cluster.merged", "cluster.main")

lapply(feature_list, function(feature_name){
  visGroup(sce, feature_name, dim_red= "tsne")
})
```

# Size/Strength of the batch effcet
How much of the variance within data can be attributed to the batch effect?

## VariancePartitioning
```{r variance part}
expr <- as.matrix(assays(sce)$logcounts)
meta_sub <- as.data.frame(colData(sce)[, c("cluster.merged", "dataset")])
form <- ~ (1|cluster.merged) + (1|dataset)

#varPart <- fitExtractVarPartModel(expr, form, meta_sub) 

#Sort variables (i.e. columns) by median fraction# of variance explained
#vp <- sortCols(varPart)
vp <- readRDS(paste0(out_path,"/vp_pbmc.rds"))
vp_names <- rownames(vp)
vp <-vp  %>% dplyr::mutate(gene= vp_names) %>% dplyr::arrange(-dataset)
vp_sub <- vp[1:3] %>% set_rownames(vp$gene)

#plot 
plotPercentBars( vp_sub[1:10,] )
plotVarPart( vp_sub )

```



Summarize variance partitioning
```{r summarize}
#How many genes have a variance component affected by the batch variable with more than 1%
n_batch_gene <- as_tibble(vp) %>%  dplyr::filter(dataset > 0.01) %>% nrow()
n_batch_gene10 <- as_tibble(vp) %>%  dplyr::filter(dataset > 0.1) %>% nrow()
n_celltype_gene <- as_tibble(vp) %>%  dplyr::filter(cluster.merged> 0.01) %>% nrow()
n_rel <- n_batch_gene/n_celltype_gene

#The mean percentage of the variance that is explained by the batch effect independent from the celltype
m_batch <- mean(vp$dataset)
m_celltype <- mean(vp$cluster.merged)
m_rel <- m_batch/m_celltype


#The median percentage of the variance that is explained by the batch effect independent from the celltype
me_batch <- median(vp$dataset)
me_celltype <- median(vp$cluster.merged)
me_rel <- me_batch/me_celltype
```


# Celltype specificity

## Celltype abundance
```{r celltype abundance}
meta_tib <- as_tibble(colData(sce)) %>% group_by(sample_type, cluster.merged) %>% summarize(n = n()) %>% dplyr::mutate(cell_freq = n / sum(n))


plot_abundance <- function(cluster_var, tib, x_var){
  meta_df <- as.data.frame(eval(tib))
  p <-ggplot(data=meta_df, aes_string(x=x_var, y="cell_freq", fill = cluster_var)) +
  geom_bar(stat="identity") + scale_fill_manual(values=cols)
  p + coord_flip() + theme_minimal()
}

plot_abundance(cluster_var = "cluster.merged", tib = meta_tib, x_var = "sample_type")
```

Test for significant changes in celltype abundances. Diffcyt (skip for datasets without replicates)
```{r sum}

#colData
colData(sce)$sample_id <- colData(sce)$dataset
sce$media <- ifelse(grepl("Fresh PBMCs", sce$sample_type), "fresh", "frozen")

col_dat <-  data.frame("sample_id" = levels(sce$sample_id), "group_id" = c("fresh", rep("frozen", 3))) %>% set_rownames(levels(sce$sample_id)) 


#create desing matrix
design_ <- createDesignMatrix(
  col_dat, cols_design = c("group_id")
)

#create contrast
contrast <- createContrast(c(0, 1))

#create summarizedExperiment for cluster abundance (rows = cluster, columns= samples)
cluster_counts <- as_tibble(colData(sce)) %>% group_by(cluster.merged, sample_id) %>% summarize(n=n()) %>%  spread(sample_id, n) 
cluster_count <- as.matrix(cluster_counts[,2:5])
rownames(cluster_count) <- cluster_counts$cluster.merged

#rowData
row_dat <- as_tibble(colData(sce)) %>% group_by(cluster.merged) %>% summarize(n=n()) %>% set_colnames(c("cluster_id", "n_cells"))



se <- SummarizedExperiment(list("counts" = cluster_count), rowData= as.data.frame(row_dat), colData= col_dat)


#differential abundance
res_DA <- testDA_edgeR(se, design_, contrast)

#summarize - number of differential abundance cluster
n_da_cluster <- length(which(rowData(res_DA)$p_adj < 0.1))

```

# Count distribution
Do the overall counts distribution vary between batches? Clusterwise ploting?

```{r count distributions, fig.width = 7, fig.height = 6}
#sample an cluster ids
sids <- levels(as.factor(sce$sample_type))
names(sids) <- sids
cids <- levels(as.factor(sce$cluster.merged))
names(cids) <- cids

#mean gene expression by sample and cluster
mean_list <- lapply(sids, function(batch){
  mean_cluster <- lapply(cids, function(cluster){
    counts_sc <- as.matrix(logcounts(
        sce[,sce$sample_type %in% batch & sce$cluster.merged %in% cluster]))
  })
  mean_c <- mean_cluster %>% map(rowMeans) %>% bind_rows %>%
    dplyr::mutate(gene=rownames(sce)) %>% gather(cluster, counts, "0":"6") 
  })

mean_expr <- mean_list %>% bind_rows(.id= "sample") 

ggplot(mean_expr, aes(x=counts, colour=sample)) + geom_density(alpha=.3) + 
    theme_classic() +
    facet_wrap( ~ cluster, ncol = 3) +
    scale_colour_manual(values = cols[c(1:3,7)]) +
    scale_x_continuous(limits =  c(0, 0.4))

#number of cluster with differnt batch distributions
n_dist <- 1
```


Mean expression counts media vs fresh
```{r mean expression, fig.height=6}
  
#mean expression
sids <- levels(as.factor(sce$sample_type))
names(sids) <- sids
cids <- levels(as.factor(sce$cluster.merged))
names(cids) <- cids
  
mean_list <- lapply(sids, function(batch){
      mean_cluster <- lapply(cids, function(cluster){
        counts_sc <- as.matrix(logcounts(
          sce[,sce$sample_type %in% batch & sce$cluster.merged %in% cluster]))
      })
    mean_c <- mean_cluster %>% map(rowMeans) %>% bind_rows %>% dplyr::mutate(gene=rownames(sce)) %>% gather(cluster, counts, "0":"6") 
  })
  
  mean_expr <- mean_list %>% bind_rows(.id = "sample" ) %>% spread(sample, counts)
  colnames(mean_expr) <- c("gene", "cluster", "fresh", "CS10", "DMSO", "PSC7")
  
  lapply(c("CS10", "DMSO", "PSC7"), function(media){
    ggplot(mean_expr, aes_string(x="fresh", y=media)) + 
      geom_point(alpha=.3, aes(color=cluster)) + 
    ggtitle(media) + geom_abline(slope = 1) + coord_fixed() +
    facet_wrap( ~ cluster, ncol = 3) +
    scale_color_manual(values=cols)
  })
  
  

  
```

# Cellspecific mixing score
Calculate cms
```{r cms}
#sce <- cms(sce, group = "sample_type", k = 200, k_min = 60, cell_min = 20)
#saveRDS(sce, paste0(out_path, "/pbmc_media_cms.rds"))
sce <- readRDS(paste0(out_path, "/pbmc_media_cms.rds"))

visHist(sce, n_col = 2)
visMetric(sce, metric_var = "cms_smooth", dim_red = "tsne")

#summarize
mean_cms <- mean(sce$cms)
n_cms_0.01 <- length(which(sce$cms < 0.01))
cluster_mean_cms <- as_tibble(colData(sce)) %>% group_by(cluster.merged) %>% summarize(cms_mean = mean(cms))

var_cms <- sd(cluster_mean_cms$cms_mean)

```


# Summarize results
```{r summary}
#Size? How much of the variance can be attributed to the batch effect?
size <- data.frame("batch_genes_1per" = n_batch_gene,  
                   "batch_genes_10per" = n_batch_gene10,
                   "celltype_gene_1per" = n_celltype_gene,
                   "relative_batch_celltype" = n_rel,
                   "mean_var_batch" = m_batch,
                   "mean_var_celltype" = m_celltype,
                   "median_var_batch" = me_batch,
                   "median_var_celltype" = me_celltype)


#Celltype-specificity? How celltype/cluster specific are batch effects? Differences in sample variation between batches?
celltype <- data.frame("DA_celltypes" = n_da_cluster,
                       "n_count_dist" = n_dist,
                       "mean_cms" = mean_cms,
                       "celltype_var_cms" = var_cms,
                       "n_cells_cms_0.01" = n_cms_0.01)

#Gene-specificity? How do they effect genes? Single genes? All genes? Which genes?
#gene <- data.frame("mean_n_de_genes" = mean_n_de,
#                   "n_genes_lfc2" = n_genes_lfc2,
#                   "DE_overlap" = de_overlap,
#                   "DE_overlap50" = de_overlap50,
#                   "rel_cluster_specific_DE" = rel_spec
#                   )
# Cell-specificity? How cell-specific are batche effects? Are their differences in within celltype variation between batches?

summary <- cbind(size, celltype )#, gene) %>% set_rownames("pbmc_media_storage")
saveRDS(summary, paste0(out_path, "/summary_pbmc_media_storage.rds"))

```

